---
title: "roam: Remote Objects with Active-binding Magic"
author: Mitchell O'Hara-Wild\newline Yangzhuoran Fin Yang
titlegraphic: bg-13.png
titlecolor: white
toc: false
keep-tex: true
format:
  presentation-beamer: 
    template-partials:
        - before-title.tex
    include-in-header: 
      text: \newcommand{\theHtable}{\thetable}
execute: 
  eval: false
  echo: true
---


## Including data in a package __without__ `roam`

\vspace{-20pt}

:::: {layout="[ 50,-2, 50 ]"}

::: {#1col}
::: {.callout-note}
### Package `pkg` Writer

```r
# data-raw/bee.R
library(readr)
bee <- read_csv(<bee.csv>)
usethis::use_data(bee)
```

\vspace{115pt}
<!-- \pause -->

<!-- ::: {.callout-important} -->

<!-- - Data installed with the package -->
<!-- - CRAN Size limit 5 MB -->
<!-- - Update package to update data -->
<!-- ::: -->

:::

:::

::: {.callout-tip}
### User

```{r}
#| echo: false
#| eval: true
bee <- readr::read_csv("https://raw.githubusercontent.com/finyang/roam/master/demo/bee_colonies.csv")
```
```{r}
#| eval: false
library(pkg)
bee
```
```{r}
#| eval: true
#| echo: false
print(dplyr::select(bee, -1), width = 30, n=2)
```


:::

::::

\only<2>{\begin{textblock}{6}(1.4,5)\fontsize{12}{13}\sf
\begin{alertblock}{}
\begin{itemize}
\tightlist
\item
Data included in package
\item
CRAN size limit 5 MB
\item
The data are updated only when the package is updated
\end{itemize}
\end{alertblock}
\end{textblock}
}

## Including data in a package __with__ `roam`

\vspace{-20pt}

:::: {layout="[ 50,-2, 50 ]"}

::: {#1col}
::: {.callout-note}
### Package `pkg` Writer

```r
obtainer <- function(version) 
{
  readr::read_csv(<bee.csv>)
}

bee <- roam::new_roam(
  'pkg', 'bee', obtainer)

.onLoad <- function(libname, 
                    pkgname) 
{
  roam::roam_activate(bee)
}

```

\vspace{9pt}

:::

:::

::: {.callout-tip}
### User

```{r}
#| eval: false
library(pkg)
options(roam.autodownload = TRUE)
bee
```
```{r}
#| eval: true
#| echo: false
print(dplyr::select(bee, -1), width = 30, n=1)
```


:::

::::

\only<2>{\begin{textblock}{6}(1.4,6)\fontsize{12}{13}\sf
\begin{alertblock}{}
\begin{itemize}
\tightlist
\item
Data hosted remotely
\item
No size limit
\item
Updating data without updating package
\end{itemize}
\end{alertblock}
\end{textblock}
}


## Versioning with `roam`

\vspace{-20pt}

:::: {layout="[ 50,-2, 50 ]"}

::: {#1col}
::: {.callout-note}
### Package `pkg` Writer

```r
obtainer <- function(version) {
  if(version == 'latest') 
    version <- '0.1.0'
  # Specify the version
  roam::roam_set_version(version)
  readr::read_csv(<bee-v.csv>)
}

bee <- roam::new_roam(
  'pkg', 'bee', obtainer)

.onLoad <- function(libname, 
                    pkgname) 
  roam::roam_activate(bee)

```

:::

:::

::: {.callout-tip}
### User

```r
library(pkg)
library(roam)

# Update to the latest version
roam_update(bee)

# Install a specific version
roam_install(bee, version = '0.1.0')

# Delete local cache
roam_delete(bee)

# Find currently installed version
roam_version('pkg', 'bee')
```


:::

::::

## More information

### Roadmap: Cache multiple versions

```r
library(pkg)
library(roam)

bee %v% "0.1.0"
bee %v% "0.1.1"
```

\only<2->{
\placefig{0.7}{5}{width=3.5cm}{roam}
\begin{textblock}{10.5}(4.5,4.8)
\begin{alertblock}{}\fontsize{14}{17}\sf
\textbf{Slides}: \href{https://yangzhuoranyang.com/talk/user-2024/}{yangzhuoranyang.com/talk/user-2024}

\textbf{roam}: \href{https://github.com/FinYang/roam}{github.com/FinYang/roam}

\href{https://yangzhuoranyang.com}{\faIcon{home}  yangzhuoranyang.com}

\href{https://github.com/finyang}{\faIcon{github}  @finyang}

\href{mailto:fin.yang@monash.edu}{\faIcon{envelope} fin.yang@monash.edu}
\end{alertblock}
\end{textblock}
}
